### 2021-09-10 sections/appendix/descrete_event_simulation/main.tex
Add first draft of how-to guide

This model will be studied by using  
\lstinline[style=pystyle]{ambulance_game}.
Install the created library in your python environment, by running the 
following command in the command line:
\begin{lstlisting}[language=bash, style=terminalstyle]
    $ pip install ambulance_game
\end{lstlisting}

@@

@@

\subsection{Explanation}

>>>>

This model will be studied by using  
\lstinline[style=pystyle]{ambulance_game}.
Install the created library in your python environment, by running the 
following command in the command line:
\begin{lstlisting}[style=terminalstyle]
    $ pip install ambulance_game
\end{lstlisting}

@@

The package can be installed by either running:

\begin{lstlisting}[style=terminalstyle]
    $ pip install ambulance_game
\end{lstlisting}

in the command line or via the instructions provided in the GitHub repository.
% TODO: Cite repository
The required arguments that need to be passed to the simulate\_model() function
are the following:
\begin{itemize}
    \item lambda\_1 (\(\lambda_1\)): The arrival rate of class 1 individuals.
    \item lambda\_2 (\(\lambda_2\)): The arrival rate of class 2 individuals.
    \item mu (\(\mu\)): The service rate of the servers.
    \item num\_of\_servers (\(C\)): The number of servers in the system.
    \item threshold (\(T\)): The threshold that indicates when to start blocking 
    class 2 individuals.
\end{itemize}

For every service completion Ciw stores all data records in a simulation 
object~\cite{ciwpython}.
The records that are stored are the following:

% TODO: Maybe move this to reference 
\begin{multicols}{2}
    \begin{itemize}
        \item \textbf{id\_number} \(\in R\).
        \item \textbf{customer\_class} \(= 0\)
        \item \textbf{node} \(= \{0, 1, 2, -1 \} \)
        \item \textbf{arrival\_date} \( \in R^+ \)
        \item \textbf{waiting\_time} \( \in R^+ \)
        \item \textbf{service\_start\_date} \( \in R^+ \)
        \item \textbf{service\_time} \( \in R^+ \)
        \item \textbf{service\_end\_time} \( \in R^+ \)
        \item \textbf{time\_blocked} \( \in R^+ \)
        \item \textbf{exit\_date} \( \in R^+ \)
        \item \textbf{destination} \( = \{1, 2, -1\} \)
        \item \textbf{queue\_size\_at\_arrival} \( \in N \)
        \item \textbf{queue\_size\_at\_departure} \( \in N \)
    \end{itemize}
\end{multicols}

To get the simulation object with all the data records, the following code can be
used:
\begin{lstlisting}[style=pystyle]
    >>> import ambulance_game as abg
    >>> Simulation = abg.simulation.simulate_model(
    ...     lambda_1=3,
    ...     lambda_2=2,
    ...     mu=1,
    ...     num_of_servers=6,
    ...     threshold=10,
    ... )
    >>> Simulation.get_all_records()[1]
    Record(id_number=1, customer_class=0, node=2, arrival_date=0.5391449803891563, waiting_time=0.0, service_start_date=0.5391449803891563, service_time=0.17003700443114755, service_end_date=0.7091819848203038, time_blocked=0.0, exit_date=0.7091819848203038, destination=-1, queue_size_at_arrival=0, queue_size_at_departure=0)
\end{lstlisting}

Additional arguments that can be passed to the function are:
\begin{itemize}
    \item \textit{system\_capacity}: The maximum number of individuals in 
    waiting zone 2.
    \item \textit{buffer\_capacity}: The maximum number of individuals in 
    waiting zone 1.
    \item \textit{seed\_num}: The seed number for the random number generator.
    \item \textit{runtime}: How long to run the simulation for.
\end{itemize}

From a single run of the simulation the data records can be used the get the
average for certain performance measures. 
The following code can be used to get the mean waiting time, blocking time, 
service time and the proportion of individuals within target.

\begin{lstlisting}[style=pystyle]
    >>> records = Simulation.get_all_records()
    >>> mean_wait = np.mean(
    ...     [w.waiting_time for w in records]
    ... )
    >>> mean_block = np.mean(
    ...     [b.time_blocked for b in records]
    ... )
    >>> mean_service = np.mean(
    ...     [s.service_time for s in records]
    ... )
    >>> target = 1
    >>> proportion_within_target = np.mean(
    ...     [w.waiting_time <= target for w in records]
    ... )

\end{lstlisting}

To eliminate any stochasticity in the simulation, the simulation can be run
numerous times and get the avergae performance measures out of all the runs.

\begin{lstlisting}[style=pystyle]
    >>> import numpy as np
    >>> import ambulance_game as abg
    >>> all_simulations = abg.simulation.get_multiple_runs_results(
    ...     lambda_1=3,
    ...     lambda_2=2,
    ...     mu=1,
    ...     num_of_servers=6,
    ...     threshold=10,
    ...     system_capacity=20,
    ...     buffer_capacity=10,
    ...     seed_num=0,
    ...     runtime=2000,
    ...     num_of_trials=10,
    ... )
    >>> mean_wait = np.mean([
    ...     np.mean(w.waiting_times) for w in mean_simulations
    ... ])
    >>> mean_service = np.mean([
    ...     np.mean(s.service_times) for s in mult_results
    ... ])
    >>> mean_block = np.mean([
    ...     np.mean(b.blocking_times) for b in mult_results
    ... ])
\end{lstlisting}

% TODO: Fix code for proportion of individuals within time target

% Run multiple simulation results
% Show all possible arguments
% Get all performance measures

@@

% This discrete event simulation model was built in python and can be installed by 
% running the following command in the terminal:

% Having installed the package, the following script can be used to simulate, and 
% get all required performance measures, of a queueing system with two waiting 
% spaces and two types of individuals for a runtime of 2000 unit time with the 
% following parameters:

% \lstinputlisting[language=Python, style=pystyle]{sections/appendix/descrete_event_simulation/simulation.py}

% The script above shows the outcome of the DES model for a single run.
% To minimise the stochasticity of the simulation, the model can be simulated for 
% numerous trials. 
% The following script can be used to run the simulation for a number of times 
% and get the mean of the waiting, service and blocking times:

% \lstinputlisting[language=Python, style=pystyle]{sections/appendix/descrete_event_simulation/multiple_runs.py}

% Finally, the proportion of individuals within target for multiple runs can be
% calculated by running the following block of code:

% \lstinputlisting[language=Python, style=pystyle]{sections/appendix/descrete_event_simulation/multiple_runs_proportion.py}
